### 2019-01-27 gameth1.tex
gametheory

hence to find a strictly dominant strategy one need to find $h_i^*$:
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_{-i}, \forall\ h_i
\end{align*}
Suppose $\beta = 0$ then 
\begin{align*}
u_i(h_i, h_{-i}) = \alpha\frac{h_i}{n} + \alpha\frac{h_1 + \dots+h_{i-1}+h_{i+1}+\dots+h_n}{n} - w_ih_i^2
\end{align*}
it is a quandratic function in $h_i$ and regardless of what $h_j\ \forall\ j \in\left\{1, \dots, n\right\}\setminus \left\{i\right\}$ is it attains maximum at $h_i = \frac{\alpha}{2nw_i}$. Thus, strategy $h_i = \frac{\alpha}{2nw_i}$ is a strictly dominant strategy for each firm in case $\beta = 0$. Now assume conversly that each firm has a strictly dominant strategy $h_i^*$. Then 
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \  \forall\ h_i, h_{-i}
\end{align*}
Suppose by contradiction that $\beta > 0$. Let us denote $\prod_{k \in \left\{1, \dots, n\right\}\setminus\left\{i\right\}}h_k$ as $H_{-i}$ then if for some $h_{-i}$ - profile of strategies of other players
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_i \neq h_{i}^*
\end{align*}
then $h_{i}^*$ is the extremum of the payoff function, given $H_{-i}$, i.e.
\begin{align*}
h_i^* = \frac{\alpha}{2nw_i} + \frac{\beta}{2nw_i}H_{-i}
\end{align*}
but now suppose $\forall j = 1, \dots, i-1, i+1, \dots, n$, $\hat{h_j} = \varepsilon^{\frac{1}{n-1}}h_j$ for some positive $\varepsilon$. Then
\begin{align*}
\exists\ \hat{h_i} = \frac{\alpha}{2nw_i} + \frac{\varepsilon \beta}{2nw_i}H_{-i} \neq h^*_i: u_i(\hat{h_i}, \hat{h_{-i}}) \ge u_i(h_i^*, \hat{h_{-i}})
\end{align*}
Because the value of the function at its maximum is always greater or equal than in any other point. That means that $h_i^*$ is not a strictly dominant strategy. This contradiction shows that $\beta = 0$. Q.E.D.
\section*{Problem 4}
Prove the following statement
In a finite simultaneous move game representable in normal form,
\begin{align*}
\Gamma =
(I, \times_{i \in I}S_i,(u_i)_{i\in I})
\end{align*}
if a single profile of pure strategies survives the process of iterated deletion
of strictly dominated strategies, then this profile must be the unique Nash
equilibrium of the game

@@

\end{document}

>>>>

hence to find a strictly dominant strategy one need to find $h_i^*$:
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_{-i}, \forall\ h_i
\end{align*}
Suppose $\beta = 0$ then 
\begin{align*}
u_i(h_i, h_{-i}) = \alpha\frac{h_i}{n} + \alpha\frac{h_1 + \dots+h_{i-1}+h_{i+1}+\dots+h_n}{n} - w_ih_i^2
\end{align*}
it is a quandratic function in $h_i$ and regardless of what $h_j\ \forall\ j \in\left\{1, \dots, n\right\}\setminus \left\{i\right\}$ is it attains maximum at $h_i = \frac{\alpha}{2nw_i}$. Thus, strategy $h_i = \frac{\alpha}{2nw_i}$ is a strictly dominant strategy for each firm in case $\beta = 0$. Now assume conversly that each firm has a strictly dominant strategy $h_i^*$. Then 
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \  \forall\ h_i, h_{-i}
\end{align*}
Suppose by contradiction that $\beta > 0$. Let us denote $\prod_{k \in \left\{1, \dots, n\right\}\setminus\left\{i\right\}}h_k$ as $H_{-i}$ then if for some $h_{-i}$ - profile of strategies of other players
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_i \neq h_{i}^*
\end{align*}
then $h_{i}^*$ is the extremum of the payoff function, given $H_{-i}$, i.e.
\begin{align*}
h_i^* = \frac{\alpha}{2nw_i} + \frac{\beta}{2nw_i}H_{-i}
\end{align*}
but now suppose $\forall j = 1, \dots, i-1, i+1, \dots, n$, $\hat{h_j} = \varepsilon^{\frac{1}{n-1}}h_j$ for some positive $\varepsilon$. Then
\begin{align*}
\exists\ \hat{h_i} = \frac{\alpha}{2nw_i} + \frac{\varepsilon \beta}{2nw_i}H_{-i} \neq h^*_i: u_i(\hat{h_i}, \hat{h_{-i}}) \ge u_i(h_i^*, \hat{h_{-i}})
\end{align*}
Because the value of the function at its maximum is always greater or equal than in any other point. That means that $h_i^*$ is not a strictly dominant strategy. This contradiction shows that $\beta = 0$. Q.E.D.
\section*{Problem 4}
Prove the following statement

In a finite simultaneous move game representable in normal form,
\begin{align*}
\Gamma =
(I, \times_{i \in I}S_i,(u_i)_{i\in I})
\end{align*}
if a single profile of pure strategies survives the process of iterated deletion
of strictly dominated strategies, then this profile must be the unique Nash
equilibrium of the game

@@

First of all let us prove that the survived strategy is indeed a Nash equilibrium, after that let us prove that none of Nash equilibria can be deleted over the iterated deletion process.

Assume by contradiction that the profile is not a Nash equilibrium, i.e. for some player $i$, $s_i^*$ is not a best response on $s^*_{-i}$. That means that the best response $\hat{s_i}$ has been deleted through the process of iterated deletion. Let us consider the step when it occured. To be deleted there must exist a strategy $\tilde{s_i}$ such that
\begin{align*}
\forall\ s_{-i} \text{ which has survived until this step and for } s^*_{-i} \text{ in particular }\to u_i(\tilde{s_i}, s_{-i}) > u_i(\hat{s_i}, s_{-i})
\end{align*}
but that means that $\hat{s_i}$ is not a best response on $s^*_{-i}$. The contradiction shows that $s^*_{i}$ is indeed a best response for each player $i$, hence the profile is a Nash equilibrium.

It remains to show that none of Nash equilibria can be deleted through the process of iterated deletion. Assume by contradiction that some Nash equilibrium $(s_1^*, \dots, s_I^*)$ has been deleted, wlog that means that for some player $i$, $s_i^*$ has been deleted as a strictly dominated strategy (while $s_{-i}^*$ has still not be deleted). That means that
\begin{align*}
\exists\ \hat{s_i} \in S_i:\ \forall\ s_{-i} \text{ and for } s_{-i}^* \text{ in particular }\to u_i(\hat{s_i}, s_{-i}) > u_i(s_i^*, s_{-i})
\end{align*}
but that means that $s_{i}^*$ cannot be a best response on $s_{-i}^*$ hence it cannot be part of the Nash equilibium. This contradiction shows that none of Nash equilibria can be deleted. Q.E.D.
\end{document}
